\nsection{Life Wars}

Inspired by the classic game, {\it Core Wars}
\wwwurl{http://en.wikipedia.org/wiki/Core_War}
here we look at a two player version of Conway's 
Game of Life.

In our game, each of two `players' submit
a Life 1.06 file and cells from these inserted into an
empty board. The cells are coded based on which player
created them (say `+' and `@'). The game is then run, and
the player having most cells left after a fixed number of
iterations, over many games, is deemed the winner.

The rules are~:
\begin{enumerate}
\item The board is $150$ cells wide, and $90$ cells tall.
\item The board is toroidal; that is, it wraps around from the left
edge to the right, and the top to the bottom.
\item Each player can submit a Life 1.06 file that is maximum of $100$
lines long, {\bf including} the header line.
\item Since each of the Life 1.06 files describe absolute positions
for cells, each player is assigned a random origin for their cells. 
If there is any collision when attempting to add the cells initially
(i.e. both players happen to specify a cell in the same square),
then new origins are chosen randomly and the process begun from scratch.
\item The `standard' B3/S23 rules are used.
\item The colour of cells is never taken into account (i.e. cells are still either `alive' or `dead').
The sole exception to this is that when a cell is born, it takes the colour of the majority its
neighbours.
\item There are $5000$ generations played every game.
\item A running count of how many cells each player has left at the end
of each game is kept. The board is cleared and the next game randomly
restarted.
\item There are $50$ games run in total.
\item The player with the highest number of cells over all $50$ games
is the winner.
\end{enumerate}

It's easy to extend these rules, of course, to allow for three or more players,
but it's unclear for three players what would happen in the majority vote if there
was a draw (i.e. a new cell is born based on three cells around it, one belonging
to each player.  Other rule variants are also possible
(e.g. {\it Highlife} (B36/S23),
but once again, the birth rule for $3$ or $6$ neighbours would cause majority
voting issues for two and three players.

\begin{exercise}
Write  a program that accepts two Life 1.06 files and reports which of them is the winner.
The first few games might look like:
\begin{terminaloutput}
% /lifewars blinkerpuffer2.lif bigglider.lif 

        0    50    12  Player 1
        1   370   141  Player 1
        2   437   281  Player 1
        3   450   602  Player 2
        4   540   623  Player 2
        5   991   629  Player 1
        6  1063   674  Player 1
        7  1211   707  Player 1
        8  1263   735  Player 1
        9  1358   758  Player 1
.
.
.
    Player 1 wins by 7857 cells to 2373 cells
\end{terminaloutput}
\end{exercise}
